ms_8

### 2020-04-26 ms_8.Rmd
almost finished. Need to add food access and fix model

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(janitor)
library(readr)
library(readxl)
library(lubridate)
library(stringr)
library(gganimate)
library(ggplot2)
library(usmap)
library(maps)
library(gganimate)
library(scales)
library(infer)
library(broom)
library(tidyverse)
library(ggcorrplot)
library(gt)
```

@@

food_poverty_mean_plot <- plot_usmap(data = food_poverty_mean, values = "mean_poverty", 
                                     color = "white", labels = FALSE) +
    theme(legend.position = "right",
          plot.title = element_text(hjust = 0.5)) + 
    scale_fill_continuous(low = "white", high = "blue", name = "Mean Poverty Rate") +
    labs(title = "Poverty Rate in the US",
         caption = "Data from US Department of Agriculture and 2010 Census Bureau") +
    theme_void()
food_poverty_mean_plot

@@

joined <- joined %>% 
    ungroup() %>% 
    mutate(age = as.factor(age),
           gender = as.factor(gender),
           race = as.factor(race),
           urban = as.factor(urban),
           region = as.factor(region))

@@

@@

gtsave(joined_lm_lia_gt, "lia_gt.html")

@@

joined_poverty_obesity <- bootstrap_joined %>% 
  ggplot(aes(x = mean_poverty, y = mean_perc_obese)) +
  geom_jitter(aes(color = urban)) +
  scale_color_manual(values = c("purple", "dark red")) +
  theme_minimal() +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank()) +
  labs(title = "Poverty Rate on Obesity Rate",
       caption = "Data from US Department of Agriculture and 2010 Census Bureau",
       color = "Ruralness",
       x = "Mean Poverty Rate",
       y = "Mean Obesity Rate") +
  geom_smooth(method = "lm", color = "black")
joined_poverty_obesity

@@

Food lia
Could allow people to choose between which regions they want to compare

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(janitor)
library(readr)
library(readxl)
library(lubridate)
library(stringr)
library(gganimate)
library(ggplot2)
library(usmap)
library(maps)
library(gganimate)
library(scales)
library(infer)
library(broom)
library(tidyverse)
library(ggcorrplot)
library(gt)
library(webshot)
```

@@

food_poverty_mean_plot <- plot_usmap(data = food_poverty_mean, values = "mean_poverty", 
                                     color = "white", labels = FALSE) +
    theme(legend.position = "right",
          plot.title = element_text(hjust = 0.5)) + 
    scale_fill_continuous(low = "white", high = "blue", name = "Mean Poverty Rate") +
    labs(title = "Poverty Rate in the US",
         caption = "Data from US Department of Agriculture and 2010 Census Bureau") +
    theme_void()

@@

joined <- joined %>% 
    ungroup() %>% 
    mutate(age = as.factor(age),
           gender = as.factor(gender),
           race = as.factor(race),
           urban = as.factor(urban),
           region = as.factor(region))
saveRDS(joined, file = "./obesity_shiny/data/joined.RDS")

@@

saveRDS(joined_cor, file = "./obesity_shiny/data/joined_cor.RDS")

@@

gtsave(joined_lm_lia_gt, "lia_gt.png")

@@

joined_poverty_obesity <- bootstrap_joined %>% 
  ggplot(aes(x = mean_poverty, y = mean_perc_obese)) +
  geom_jitter(aes(color = urban)) +
  scale_color_manual(values = c("purple", "dark red")) +
  theme_minimal() +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank()) +
  labs(title = "Poverty Rate on Obesity Rate",
       caption = "Data from US Department of Agriculture and 2010 Census Bureau",
       color = "Ruralness",
       x = "Mean Poverty Rate",
       y = "Mean Obesity Rate") +
  geom_smooth(method = "lm", color = "black")

joined_demo <- bootstrap_joined %>% 
  ggplot(aes(x = age, y = mean_perc_obese, color = age)) +
  geom_jitter() +
  theme_minimal() +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(angle = 35, hjust = 1)) +
  labs(title = "Poverty Rate on Obesity Rate",
       caption = "Data from US Department of Agriculture and 2010 Census Bureau",
       color = "Ruralness",
       x = "Mean Poverty Rate",
       y = "Mean Obesity Rate")
joined_demo

@@

Food Access
Food lia
Could allow people to choose between which regions they want to compare
Food lia us map
Allow people to choose between lia and la
